True versus apparent shapes of astrophysical bow shocks

### 2016-09-29 papers/Paper1/sec-application.tex
Edit applications section, enhance apperance of proplyd's shell circle fit

With the data from figure \ref{fig:conic-xi}, we derived a set of models which assumes a given set of bow shock parameters $(\beta, i,\xi)$ and have agreement with the measurements of each proplyd. A given model predicts the no projected
distance $D$ for the proplyd and the non projected radius $R_0$. We summarize the results of the models in table \ref{tab:arc-fits}.

From this models also we can estimate the stellar ionizing flux required to have ionization balance with the photoevaporated flow. To do this estimation we used the measured ionization front radius and the photoevaporated flow density for each proplyd
and incorporated them into the models. The result is shown in figure \ref{fig:pressure} at top. We highlight the models which have agreement with ionization balance.
Also we can estimate the stagnation pressure of the photoevaporated flow. The result is shown in figure \ref{fig:pressure} at bottom. 
From this figures we can see that our models predict that for the farthest proplyds (169-338, 177-341 and 180-331) the stellar wind pressure is weaker than the estimated stagnation pressure. Since these bow shocks are stationary, we expect pressure
balance, so the stellar wind is not enough to guarantee pressure balance far from \thC{}

@@

\begin{figure*}
  \setkeys{Gin}{width=0.33\linewidth, trim=10 30 55 62.5}
\begin{tabular}{@{}c@{}c@{}c@{}}

>>>>

With the data from figure \ref{fig:conic-xi}, we derived a set of models which assumes a given set of bow shock parameters $(\beta, i,\xi)$ which have agreement with the measurements of 
each proplyd. A given model predicts the non projected distance $D$ for the proplyd and the non projected radius $R_0$. 
We summarize the results of the models in table \ref{tab:arc-fits}.

From this models also we can estimate the stellar ionizing flux required to have ionization balance with the photoevaporated flow. 
To do this estimation we used the ionization front radius and the photoevaporated flow density measured in \citet{HA:1998} for each proplyd
and incorporated them into the models. The result is shown in figure \ref{fig:pressure} at top. We highlight the models which have agreement with ionization balance.
Also we can estimate the stagnation pressure of the photoevaporated flow. The result is shown in figure \ref{fig:pressure} at bottom. 
From this figures we can see that our models predict that for the farthest proplyds (169-338, 177-341 and 180-331) the stellar wind pressure is weaker than the estimated stagnation pressure. Since these bow shocks are stationary, we expect pressure
balance, so the stellar wind is not enough to guarantee pressure balance far from \thC{}

@@

\begin{figure*}
  \setkeys{Gin}{width=0.33\linewidth}%, trim=10 30 55 62.5}
\begin{tabular}{@{}c@{}c@{}c@{}}

### 2016-09-29 papers/Paper1/sec-conclusions.tex
Include POS projection figure in section 3
And brief discussion in text
Edit applications section, enhance apperance of proplyd's shell circle fit

\section{Application to proplyd bowshocks}
\label{sec:application}

>>>>

\section{Conclusions}
\label{sec:conc}

%\newcommand\thC{\(\theta^1\)\,Ori~C}
\defcitealias{Canto:1996}{CRW}

We developed a method to estimate the shape of a generic bow shock product of the
interaction of two winds and was applied to the proplyds in the core of the ONC.
We started measuring the projected characteristic radii $(R'_0,R'_c)$ for each proplyd in our
sample and compare them with the ``conic equivalent'' of a two winds interaction model based 
on \CRW{} work to estimate the intrinsic bow shock shape and get the ionizing flux for ionization balance 
and the stagnation pressure for our sample of proplyds.
Most results are consistent with a proplyd's photoevaporated flow with an anisotropic density
distribution, with different anisotropy degrees. We ound that LV4 has the least anisotropic flow,
while LV2 has the most anisotropic flow. And for the 177-341, 169-348 and 180-331 we found out that 
the stellar wind is not enough to keep their bow socks stationary.
